\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[scale=0.75]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}


% -----------------------------
% Datos personales
% -----------------------------
\name{Matihus}{Molina Larios}
\address{Lima, Per\'u}{}
\email{matihus.molina@unmsm.edu.pe}
\social[linkedin]{maticus}
\social[github]{Maticus-7}

% -----------------------------
\begin{document} 
	\makecvtitle
	
	% -----------------------------
	% Perfil profesional
	% -----------------------------
	\section{Professional Profile}
	\cvitem{}{ I am a final-year mathematics student at National University of San Marcos with interest in Ergodic Theory, Mathematical applications to health, and Formally verified mathematics. 
		Recently, I have developed a particular interest in the formalization of mathematics using LEAN4. I am also involved in the preparation of research papers related to machine learning applied to lung cancer and a comparative study of numerical methods for differential equations of Lane-Emden type.
		My current objective is to strengthen my training in pure and applied mathematics and contribute to the development of the academic community in Peru. After graduating, I aspire to pursue postgraduate studies abroad exploring different areas of mathematics.}
	
	% -----------------------------
	% Educación
	% -----------------------------
	\section{Education}
	\cventry{03/2022 -- 12/2026 (expected)}{B.Sc. Student in Mathematical Sciences}{Universidad Nacional Mayor de San Marcos}{Lima, Per\'u}{}{Cumulative (CGPA): 15.19/20}
	\cventry{2018 -- 2021}{Graduate , English Program}{Cultural Center LIDEMPER\'U}{Lima, Per\'u}{}{}
	
	% -----------------------------
	% Idiomas
	% -----------------------------
	\section{Languages}
	\cvitem{Spanish}{Native}
	\cvitem{English}{Intermediate (B1)}
	\cvitem{Portuguese}{Basic (A2)}
	
	% -----------------------------
	% Proyectos académicos
	% -----------------------------
	\section{Academic Projects}
	\cventry{01/2025 -- 03/2025}{Proyect: ``A First Encounter with Chaotic Dynamical Systems''}{PICV-UNMSM}{}{}{
		\begin{itemize}
			\item Academic advisor: Dr. Jorge L. Crisóstomo
			\item Study of topological conjugacy between $Q_c$ and the Bernoulli Shift.
			\item Aplication of concepts from differential equation,funcional analysis,topology,and geometry.
			\item \href{http://bit.ly/3Hj8NvJ}{Click here}
	\end{itemize}}
	
	%\cventry{02/2025 -- 03/2025}{Depression Prediction in University Students}{Course: Mathematics for ML and DS (UNMSM)}{}{}{
	%	\begin{itemize}
	%		\item Application of probability ,statistics, and ML techniques .
	%		\item Supervised modeling using Python and scikit-learn.
	%		\item \href{https://github.com/Maticus-7/Mental-Healthy/tree/2bc0dac3f89d9187dfa37b6cd963d69256551167/Depression/University}{Click here}
%	\end{itemize}}
	
	\cventry{10/2025 --12/2025}{Numerical solution for differential equations of Lane-Emden type}{Stellar Structure Modeling}{}{}{
		\begin{itemize}
			\item Analysis of decomposition methods and their differences. 
			\item Numerical implementation and evaluation of the efficienty of these methods. 
			\item \href{https://github.com/Maticus-7/lane-emden}{Click here}
	\end{itemize}}
	
	% -----------------------------
	% Eventos académicos
	% -----------------------------
	\section{Academic Events} 
	%\cventry{August 2025}{PUCP -- Lima}{XXXVIII Colloquium of the Peruvian Mathematical Society}{}{}{Attendance at talks on topology, functional analysis, differential geometry, dynamical systems, and other current research topics. This event provided an excellent opportunity to learn about the work of national and international mathematicians and to engage in discussions with distinguished researchers and professors.}
	
	\cventry{October 2025}{UBB- Concepción}{E'(UBB) = 2025}{}{}{My first international academic experience. I greatly enjoyed the city and the opportunity to learn about a different culture. This experience motivated my interest in pursuing a master's degree abroad.}
	
	\cventry{December 2025}{UNASAM- Huaráz}{VII EICM}{}{}{This was my first experience presenting a research project at an event of this scale. The project presented focused on stellar structure modeling via Lane--Emden type equations.}
	
	\cventry{Febrary 2026}{UNT -- Trujillo}{Summer School and Workshop on Optimization and Operator Learning}{}{}{I participated in this important event, putting my knowledge of optimization theory and programming to the test.}
	
	% -----------------------------
	% Research interests 
	% ----------------------------- 
	\section{Research Interests} \cvitem{Pure Mathematics}{ \begin{itemize} 
			\item Functional analysis. 
			\item Ergodic theory. 
			\item Mathematical foundations of artificial intelligence. 
			\item Formally Verified Mathematics. 
			\item Mathematical applications to human health. \end{itemize}}
	
	\cvitem{Technologies}{ \begin{itemize} 
			\item Programming languages: Python, R, MATLAB,LEAN4. 
			\item Libraries: NumPy,SciPy,Pandas, Scikit-Learn, Matplotlib,PyTorch. 
			\item Tools: Git, \LaTeX. \end{itemize}}
		
	% ------------------------------
	% Logros
	% ------------------------------
	\section{Grants, Distinctions}
		\cvitem{}{BECA PERMANENCIA 2025 ,PRONABEC}
		\cvitem{}{Recognition from my faculty for my ACADEMIC EXCELLENCE}  
		
	
	% ----------------------------- 
	% Extracurricular activities 
	% -----------------------------
	\section{Extracurricular Activities} 
	\cvitem{}{Co-Director of the IEEE Computational Intelligence Society project area -- UNMSM.} 
	\cvitem{}{Former member of the cultural and artistic salsa group SALSUNI -- UNMSM.} 
	\cvitem{}{Former member of the university judo team -- UNMSM}
	\cvitem{}{Active member of the BILDHEIT.}
	
	% ----------------------------- 
	% Certificates 
	% ----------------------------- 
	\section{Certificates} 
	\cvitem{}{ \href{https://maticus-7.github.io/Certificates/}{Certificates of coursework,academic achievements are available in the following repository}.}
	
	
	
	
	
	
	
\end{document}
